Simulation Study: Null Settings

### 2018-07-23 datasets/simulations/simulations-null.Rmd
Fix t11 null sim output file names

```{r t11-run-simulation}
if (file.exists(tdist_file)) {
    res <- readRDS(tdist_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplust, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist_file)
}
```

>>>>

```{r t11-run-simulation}
if (file.exists(tdist11_file)) {
    res <- readRDS(tdist11_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplust, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = tdist11_file)
}
```
